Potential Factors of Decreasing Birth Rates in the US since the Great Recession and Beyond

### 2024-02-01 outputs/paper/paper.qmd
Update paper.qmd

# Introduction

>>>>

#### #### 
The results section should convey findings.
The discussion should include three or four sub-sections that each focus on an interesting point, and there should be another sub-section on the weaknesses of your paper, and another on potential next steps for it.
In the discussion section, and any other relevant section, please be sure to discuss ethics and bias, with reference to relevant literature.
#### ####
 data, results, discussion, and references.
# Introduction
